Fractional Types

### 2019-11-21 fracGC/p.tex
fix typo

Before before the abstract machine for the full system with
fractionals, we introduce some of the common technical details in the
simpler setting of the core $\Pi$ language. First two simple facts
about cardinalities:

\PIFMEMsize{}

>>>>

Before the abstract machine for the full system with
fractionals, we introduce some of the common technical details in the
simpler setting of the core $\Pi$ language. First two simple facts
about cardinalities:

\PIFMEMsize{}  % maybe we should use \PIMEMcard here?
